### 2018-05-24 dataset.tex
new changes to final submission

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-02}
    \caption{Validation results obtained by \citet{Taborda_2014_BSSA} in the form of GOF values across the region of interest obtained from comparisons between simulations for three different velocity models and data recorded at ground motion monitoring stations. The distribution of the results at the bottom show the count of stations on the GOF scale defined by \citet{Anderson_2004_Proc} and the ranges of the validation categories: poor, fair, good and excellent. The color version of this figure is available only in the electronic edition.}
    \label{fig:ref-gof-maps}
\end{figure*}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-03}
    \caption{Statistical distribution of the GOF dataset obtained from \citet{Taborda_2014_BSSA} shown in the form of box-plots for each metric (C1 through C11, see Table \ref{tab:metrics}), velocity model (CVM-S, CVM-H, and CVM-H+GTL), and components of motion (NS, EW, UD). In each case, the boxes represent the interquartile range ($\mathrm{IQR} = \mathrm{Q}3 - \mathrm{Q}1$), the medians are indicated by a notch in the boxes, and the vertical lines show the range of the data, with outliers (data less than $\mathrm{Q}1 - 1.5 \mathrm{IQR}$ and greater than $\mathrm{Q}3 + 1.5 \mathrm{IQR}$) shown as scattered dots. The color version of this figure is available only in the electronic edition.}
    \label{fig:data-box-plot}
\end{figure}

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-02}
    \caption{Validation results obtained by \citet{Taborda_2014_BSSA} in the form of GOF values across the region of interest obtained from comparisons between data recorded at ground motion monitoring stations and simulations for three different velocity models: \textbf{(a)} CVM-S, \textbf{(b)} CVM-H, and \textbf{(c)} CVM-H+GTL. The distribution of the results at the bottom show the count of stations on the GOF scale defined by \citet{Anderson_2004_Proc} and the ranges of the validation categories: poor, fair, good and excellent. The color version of this figure is available only in the electronic edition.}
    \label{fig:ref-gof-maps}
\end{figure*}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-03}
    \caption{Statistical distribution of the GOF dataset obtained from \citet{Taborda_2014_BSSA} shown in the form of box-plots for each metric (C1 through C11, see Table \ref{tab:metrics}), and components of motion (NS, EW, UD), for the simulations done with velocity models: \textbf{(a)} CVM-S, \textbf{(b)} CVM-H, and \textbf{(c)} CVM-H+GTL. In each case, the boxes represent the interquartile range ($\mathrm{IQR} = \mathrm{Q}3 - \mathrm{Q}1$), the medians are indicated by a notch in the boxes, and the vertical lines show the range of the data, with outliers (data less than $\mathrm{Q}1 - 1.5 \mathrm{IQR}$ and greater than $\mathrm{Q}3 + 1.5 \mathrm{IQR}$) shown as scattered dots. The color version of this figure is available only in the electronic edition.}
    \label{fig:data-box-plot}
\end{figure}

### 2018-05-24 results.tex
new changes to final submission

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06}
	\caption{Statistical distribution of the dataset as partitioned into the four validation categories (poor, fair, good, excellent) after the clustering analysis. The distributions are shown in the form of box-plots for each metric (C1 through C11). In each case, the medians are indicated by a notch in the boxes of the central quartiles, and the vertical lines represent the interquartile range, with outliers shown as scattered dots. The dashed lines and background shadows represent the boundaries of the poor, fair, good, and excellent categories as defined by \citet{Anderson_2004_Proc}. The color version of this figure is available only in the electronic edition.}
	\label{fig:boxed-clusters}
\end{figure*}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06}
	\caption{Statistical distribution of the dataset after the clustering analysis, as partitioned into the four validation categories: \textbf{(a)} poor, \textbf{(b)} fair, \textbf{(c)} good, and \textbf{(d)} excellent. The distributions are shown in the form of box-plots for each metric (C1 through C11). In each case, the medians are indicated by a notch in the boxes of the central quartiles, and the vertical lines represent the interquartile range, with outliers shown as scattered dots. The dashed lines and background shadows represent the boundaries of the poor, fair, good, and excellent categories as defined by \citet{Anderson_2004_Proc}. The color version of this figure is available only in the electronic edition.}
	\label{fig:boxed-clusters}
\end{figure*}

### 2018-05-24 testing.tex
new changes to final submission

\begin{figure*}[th!]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-11}
	\caption{Comparison of GOF validation scores obtained using an 11-metric \citet{Anderson_2004_Proc}-type GOF scoring (left) and the T1 combination GOF validation classification (right). The top plots show maps with a distribution of the scores or classes outcome at each station. The contours are drawn for illustration purposes only. The bottom plots show histograms with the count of stations for each GOF score interval or validation class. On the right-hand side, the results of both methods are compared by superimposing the results of the counts from using \citeauthor{Anderson_2004_Proc}'s method (dashed-line empty bars) next to those obtained using the T1 algorithm (filled bars). The color version of this figure is available only in the electronic edition.}
	\label{fig:avg-gof-maps}
\end{figure*}

>>>>

\begin{figure*}[th!]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-11}
	\caption{Comparison of GOF validation scores obtained using \textbf{(a)} an 11-metric \citet{Anderson_2004_Proc}-type GOF scoring, and \textbf{(b)} the T1 combination GOF validation classification. In both cases, the top plots show maps with a distribution of the scores or classes outcome at each station, where the contours are drawn for illustration purposes only; while the bottom plots show histograms with the count of stations for each GOF score interval or validation class. On the right-hand side, the results of both methods are compared by superimposing the results of the counts from using \citeauthor{Anderson_2004_Proc}'s method (dashed-line empty bars) next to those obtained using the T1 algorithm (filled bars). The color version of this figure is available only in the electronic edition.}
	\label{fig:avg-gof-maps}
\end{figure*}
